\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2020-12-18 popl-2019-journal-v/discussion.tex
Fix some more issues, improve writing in section 4.2.

\subsection{Support for source language idioms and features}

@@

  Also interesting is the idiom of passing stack references in calls, as is common in programming languages with a C-like calling convention.
  \stktokens{} supports stack references but with a couple of caveats.
  First of all, the stack capability is linear, so all references to the stack have to be linear.
  This means that the callee has to treat references linearly.
  Next, like the stack capability, the stack references must be given back to the caller on return, so they can reconstruct their original stack capability (which allows them to return). 
  Finally, the encapsulated local stack frame should be a continuous piece of memory (because it has to be addressable by a single capability: the data part of the return capability pair).
  Because of this, stack-allocated objects for which references are passed to callees must be allocated at the top or bottom of the caller's stack frame.
  An escape analysis could be used to statically determine where to put allocations and, in principle, the allocations could be reordered dynamically before a call.
  In summary, support for passing stack references as arguments to callees could be added to \stktokens{}, but this would probably require some changes in the compiler and, more importantly, would require the callee to take special care when manipulating such references.
  We are unsure whether it is realistic to apply this approach for existing C code.
\end{jversion}

>>>>

\subsection{Support for source language idioms and features}
\label{sec:supp-source-lang}

@@

  Also interesting is the idiom of passing stack references in calls, as is common in programming languages with a C-like calling convention.
  \stktokens{} supports stack references but with a couple of caveats.
  First of all, the stack capability is linear, so all references to the stack have to be linear.
  This means that the callee has to treat references linearly.
  Next, like the stack capability, the stack references must be given back to the caller on return, so they can reconstruct their original stack capability (which allows them to return). 
  Finally, the encapsulated local stack frame should be a continuous piece of memory (because it has to be addressable by a single capability: the data part of the return capability pair).
  Because of this, stack-allocated objects for which references are passed to callees must be allocated at the top or bottom of the caller's stack frame.
  An escape analysis could be used to statically determine where to put allocations and, in principle, the allocations could be reordered dynamically before a call.
  In summary, support for passing stack references as arguments to callees could be added to \stktokens{}, but this would probably require some changes in the compiler and, more importantly, would require the callee to take special care when manipulating such references.
  We are unsure whether it is realistic to apply this approach for existing C code.

  \stktokens{} relies on an important property: the fact that return seals should be uniquely associated to a single call-site.
  If we were to use a single return seal for multiple call-site, that would allow an adversary to combine a valid return data capability with a return code capability for the wrong call-site, thus breaking WBCF guarantees.
  This property is currently enforced statically in the well-formedness property for components' code memory (see Section~\ref{sec:well-form-reas}), specifically in the \texttt{C-Instr} rule.
  For any call instruction in trusted components' code memory, it is required that the return seal used is exclusively owned by this call-site.

  To guarantee that this property does not just hold when the system is initialized, but continues to hold during execution, the well-formedness judgement additionally enforces a Write-Xor-Execute policy for components:
  writable capabilities are not allowed for code memory and executable capabilities are not allowed for data memory.
  Although this approach works, it has the side effect of disallowing any form of dynamic code generation.
  This is unfortunate, because we believe that in principle, \stktokens{} is compatible with dynamic code generation, as long as the generated code respects the unique allocation of return seals to call sites.

  To lift this restriction, an alternative approach would be to enforce the unique allocation of return seals to trusted call sites semantically rather than statically.
  More concretely, the semantic reasonability requirement for components could additionally require that during any execution, a component uses a return seal only for a single call-site.
  Such an approach would, we think, obviate the need for the Write-Xor-Execute policy and the static enforcement of proper use of return seals.
  Thus, we think dynamic code generation could be allowed without losing \stktokens{} guarantees.
\end{jversion}
